Carbonate chemistry at Ny-Ålesund

### 2021-03-16 awipev-CO2.Rmd
impact of K1K2 using mean values; minor adjustements

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```

@@

## Impact of choice of constants
### Using mean values
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# impacts using pco2 and AT
carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const)
```
### Using all values pCO2 and at_calc

```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
d_ls <- d_all %>% 
  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s)
d_ls <- bind_cols(d_ls, diff_ls)

# plot
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

print(p) #p_sal_fb_ctd
```

>>>>

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

@@

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
  geom_text( aes(color=factor(monthd))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```

@@

## Impact of choice of constants
### Lueker vs Sulpis using means of monthly means
```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
monthly_means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
means <- monthly_means %>% 
  summarise(across(
    .cols = is.numeric, 
    .fns = mean, na.rm = TRUE, 
    .names = "{col}"
  ))

mean_ct <-  mean(monthly_means$mean_ct)
mean_at_calc <-  mean(monthly_means$mean_at_calc)
mean_pco2_calc <-  mean(monthly_means$mean_pco2_calc)
mean_sal <-  mean(monthly_means$mean_sal)
mean_temp <-  mean(monthly_means$mean_temp)
# impacts using pco2 and AT pair
carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")
```
The means used are:
`r knitr::kable(means, format = "simple")`

### Lueker vs Sulpis using all values pCO2 and at_calc
One uses the pair pCO2-AT

```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
tmp <- d_all %>% 
  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    tmp$pco2_fb,
    tmp$at_calc * 1e-6,
    S = tmp$sal_fb,
    T = tmp$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    tmp$pco2_fb,
    tmp$at_calc * 1e-6,
    S = tmp$sal_fb,
    T = tmp$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s) %>% 
  dplyr::select(pH, pCO2, DIC, OmegaAragonite)
diff_ls_quant <- bind_rows(
  quantile(diff_ls$pH), quantile(diff_ls$pCO2), quantile(diff_ls$DIC * 1e6), 
  quantile(diff_ls$OmegaAragonite)) %>% 
  dplyr::mutate(Variable = c("pH", "pCO2", "DIC", "OmegaAragonite"), .before = 1)
pander(diff_ls_quant)

lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
